---
title: "p8105_hw1_js5431"
author: "J Shearston"
date: "September 13, 2018"
output: 
  github_document:
    toc: true
---

```{r set_up, include = FALSE}
library(tidyverse)
```

##Problem 1

####Creating variables

Creating a random sample variable

```{r}
ran_sam = rnorm(10, 0, 5)
```

Creating a logical vector

```{r}
bigger2 = ran_sam > 2
```

Creating a character vector

```{r}
animal = c("fish", "dog", "cat", "dolphin", "elephant", "dog", "cow", "fish", "fish", "dolphin")
```

Creating a factor vector

```{r}
animal_f = factor(animal)
```

####Creating a data frame comprised of the above four vectors

```{r}
p1_df = tibble(
  ran_sam,
  bigger2,
  animal,
  animal_f
  )
```

####Taking the mean of each variable in the data frame

```{r}
mean(p1_df$ran_sam)
mean(p1_df$bigger2)
```

Notes: I am able to take the mean of the ran_sam (random sample variable) and bigger2 (logical vector) variables becuase they are both numeric, but not the animal or animal_f variables becuase they are character vectors.

####Applying the `as.numeric` function

```{r, eval = FALSE}
as.numeric(p1_df$bigger2)
as.numeric(p1_df$animal)
as.numeric(p1_df$animal_f)
```

Notes: The logical and factor variables can be coerced, while using the `as.numeric` function on the character variable results in NA for each observation. This occurs because the logical and factor variable both already have a numeric component of some type, while the character variable does not.

####Converting variable types

```{r}
factor(p1_df$animal)
as.numeric(p1_df$animal)

as.character(p1_df$animal_f)
as.numeric(p1_df$animal_f)
```

Notes: When the character variable is converted to a factor variable it is given levls, but when it is then converted to a numeric variable NA results. When the factor variable is converted to a character variable this seems to go smoothly, and can then also be transferred into a numeric variable such that each unique category in the variable is assigned a number


##Problem 2

####Creating the described dataframe

```{r data frame to graph}
x = rnorm(1000)
y = rnorm(1000)
logical = (x+y) > 0
logical_n = as.numeric(logical)
logical_f = factor(logical_n)

graphing_df = tibble(
  x,
  y,
  logical,
  logical_n,
  logical_f
  )
```

####Describing the dataset

The dataframe called "graphing_df" has a size of n=`r nrow(graphing_df)`.
The mean of x is `r mean(graphing_df$x)`, while the median is `r median(graphing_df$x)`.
The proportion of cases for which the logical vector "logical" is TRUE is `r table(logical_f)["1"]` / 1000.

####Scatterplot 1

```{r}
ggplot(graphing_df, aes(x = x, y = y, color = logical)) + geom_point()
```

####Scatterplot 2

```{r}
ggplot(graphing_df, aes(x = x, y = y, color = logical_n)) + geom_point()
```

####Scatterplot 3

```{r}
ggplot(graphing_df, aes(x = x, y = y, color = logical_f)) + geom_point()
```

####Commenting on plot colors

In Scatterplot 1, the color scale is dichotomous (true/false) because the logical variable only has two categories. However, for Scatterplot 2, the color scale is a gradient because the variable type is numeric, so instead the colors are assigned based on quartiles. Scatterplot 3 uses a binary color scale similar to Scatterplot 1, because the variable used is a factor variable and also has only two categories (this time 0/1).

####Exporting Scatterplot 1

```{r, include = FALSE}
ggplot(graphing_df, aes(x = x, y = y, color = logical)) + geom_point()
```
```{r}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```


##Problem 3

Done! js5431 on 9/18/2018
  :)

