---
title: "p8105_hw1_js5431"
author: "J Shearston"
date: "September 13, 2018"
output: github_document
---

```{r set_up, include = FALSE}
library(tidyverse)
```

##Problem 1

####Creating variables

Creating a random sample variable

```{r}
ran_sam = rnorm(10, 0, 5)
```

Creating a logical vector

```{r}
bigger2 = ran_sam > 2
```

Creating a character vector

```{r}
animal = c("fish", "dog", "cat", "dolphin", "elephant", "dog", "cow", "fish", "fish", "dolphin")
```

Creating a factor vector

```{r}
animal_f = factor(animal)
```

####Creating a data frame comprised of the above four vectors

```{r}
p1_df = tibble(
  ran_sam,
  bigger2,
  animal,
  animal_f
  )
```

####Taking the mean of each variable in the data frame

```{r}
mean(ran_sam)
mean(bigger2)
```

Notes: I am able to take the mean of the ran_sam (random sample variable) and bigger2 (logical vector) variables becuase they are both numeric, but not the animal or animal_f variables becuase they are character vectors.

####Applying the `as.numeric` function

```{r, eval = FALSE}
as.numeric(bigger2)
as.numeric(animal)
as.numeric(animal_f)
```

Notes: The logical and factor variables can be coerced, while using the `as.numeric` function on the character variable results in NA for each observation. This occurs because the logical and factor variable both already have a numeric component of some type, while the character variable does not.

####Converting variable types

```{r}
factor(animal)
as.numeric(animal)

as.character(animal_f)
as.numeric(animal_f)
```

Notes: When the character variable is converted to a factor variable it is given levls, but when it is then converted to a numeric variable NA results. When the factor variable is converted to a character variable this seems to go smoothly, and can then also be transferred into a numeric variable such that each unique category in the variable is assigned a number


##Problem 2

####Creating the described dataframe

```{r data frame to graph}
x = rnorm(1000)
y = rnorm(1000)
logical = (x+y) > 0
logical_n = as.numeric(logical)
logical_f = factor(logical_n)

graphing_df = tibble(
  x,
  y,
  logical,
  logical_n,
  logical_f
  )
```

Notes: The dataframe called "graphing_df" has a size of n=''

Write a short description of your vector using inline R code, including: * the size of the dataset * the mean and median of x * the proportion of cases for which the logical vector is TRUE


##Problem 3

Done! js5431 on 9/18/2018
:)

